Data Cleaning

### 2024-11-27 study1/analysis/1_cleaning.qmd
updating cleaning script

p_eth <- df |>
  mutate(Ethnicity = fct_relevel(Ethnicity,"East Asian", "Mixed", "White", "Black", "persian", "South Asian", "Hispanic/Latino")) |>
  ggplot(aes(x = Ethnicity)) +
  geom_bar(aes(fill = Ethnicity)) +
  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
  scale_fill_viridis_d(guide = "none") +
  labs(title = "Ethnicity", y = "Number of Participants", subtitle = "Participants per Ethnicity") +
  theme_modern(axis.title.space = 15) +
  scale_fill_manual(values = c("East Asian"="#0571B0","Mixed"= "#d01c8b", "White"="#FDB863", "Black"="#E66101", "persian" =  "#ca0020", "South Asian"="#5E3C99", "Hispanic/Latino"="#92C5DE")) +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.text.y = element_text(size = rel(1.1)),
    axis.text.x = element_text(size = rel(0.6)),
    axis.title.x = element_blank())

@@

p_country <- dplyr::select(df, region = Country) |>
  group_by(region) |>
  summarize(n = n()) |>
  right_join(map_data("world"), by = "region") |>
  ggplot(aes(long, lat, group = group)) +
  geom_polygon(aes(fill = n)) +
  scale_fill_gradientn(colors = c("#E66101", "#ca0020", "#d01c8b")) +
  labs(fill = "N") +
  theme_void() +
  labs(title = "Country of Residence", subtitle = "Number of participants by country")  +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2))
  )
p_country
```

@@

dplyr::select(df, region = Country) |>
  group_by(region) |>
  summarize(n = n()) |>
  right_join(map_data("world"), by = "region") |>
  ggplot(aes(long, lat, group = group)) +
  geom_polygon(aes(fill = n))

p_feed <- estimate_density(df$Experiment_Enjoyment) |>
  normalize(select = y) |>
  mutate(y = y * 86) |>  # To match the binwidth
  ggplot(aes(x = x)) +
  geom_bar(data=df, aes(x = Experiment_Enjoyment, fill = Condition), bins=28) +
  scale_fill_manual(values = c("Dimensions"= "#E66101","Domains" = "#ca0020", "Random"="#d01c8b")) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(title = "Experiment Enjoyment and Condition", y = "Number of Participants", color = NULL, x = "Ratings of enjoyment on a scale 1-5", subtitle = "Distribution of Participants' Experiment Enjoyment and Condition") +
  # geom_label(data = data.frame(x = mean(df$Experiment_Enjoyment) * 1.15, y = 0.95 * 75), aes(y = y), color = "red", label = paste0("Mean = ", format_value(mean(df$Experiment_Enjoyment)))) +
  theme_modern(axis.title.space = 10) +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.text.y = element_text(size = rel(1.1)),
    axis.text.x = element_text(size = rel(1.1)),
    axis.title.x = element_blank()
  )
p_feed

>>>>

p_eth <- df |>
  mutate(Ethnicity = fct_relevel(Ethnicity,"East Asian", "Mixed", "White", "Black", "persian", "South Asian", "Hispanic/Latino")) |>
  ggplot(aes(x = Ethnicity)) +
  geom_bar(aes(fill = Ethnicity)) +
  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
  scale_fill_viridis_d(guide = "none") +
  labs(title = "Ethnicity", y = "Number of Participants", subtitle = "Participants per Ethnicity") +
  theme_modern(axis.title.space = 15) +
  scale_fill_manual(values = c("East Asian"="#0571B0","Mixed"= "#d01c8b", "White"="#cc66cc", "Black"="#E66101", "persian" =  "#ca0020", "South Asian"="#5E3C99", "Hispanic/Latino"="#92C5DE")) +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.text.y = element_text(size = rel(1.1)),
    axis.text.x = element_text(size = rel(0.6)),
    axis.title.x = element_blank())

@@

p_country <- df |>
  mutate(Country = case_when(
    Country=="United States"~ "USA",
    Country=="United Kingdom" ~ "UK",
    TRUE ~ Country
  ))|>
  dplyr::select(region = Country) |>
  group_by(region) |>
  summarize(n = n()) |>
  right_join(map_data("world"), by = "region") |>
  # mutate(n = replace_na(n, 0)) |>
  ggplot(aes(long, lat, group = group)) +
  geom_polygon(aes(fill = n)) +
  scale_fill_gradientn(colors = c("#E66101", "#ca0020", "#cc66cc")) +
  labs(fill = "N") +
  theme_void() +
  labs(title = "Country of Residence", subtitle = "Number of participants by country")  +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2))
  )

p_country

```{r}
# Create mapping from df's country names to world_map's country names. I think the map is not working because the names do not match.

country_mapping <- data.frame(
  df_name = c("United States", "United Kingdom"),
  world_map = c("USA", "UK") 
)

country_mapping

@@

p_feed <- estimate_density(df$Experiment_Enjoyment) |>
  normalize(select = y) |>
  mutate(y = y * 86) |>  # To match the binwidth
  ggplot(aes(x = x)) +
  geom_bar(data=df, aes(x = Experiment_Enjoyment, fill = Condition), bins=28) +
  scale_fill_manual(values = c("Dimensions"= "#E66101","Domains" = "#ca0020", "Random"="#d01c8b")) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(title = "Experiment Enjoyment and Condition", y = "Number of Participants", fill = " ", x = "Ratings of enjoyment on a scale 1-5", subtitle = "Distribution of Participants' Experiment Enjoyment and Condition") +
  # geom_label(data = data.frame(x = mean(df$Experiment_Enjoyment) * 1.15, y = 0.95 * 75), aes(y = y), color = "red", label = paste0("Mean = ", format_value(mean(df$Experiment_Enjoyment)))) +
  facet_wrap(~Condition) +
  theme_modern(axis.title.space = 10) +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.text.y = element_text(size = rel(1.1)),
    axis.text.x = element_text(size = rel(1.1)),
    #axis.title.x = element_blank()
  )
p_feed
